The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
tidy net mets

For each multilayer network, we calculated four metrics.These included:
multidegree, graph strength, redundancy/relevance, and  layer similarity.  GOING
TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON
EXPLAINING THESE).

ALR: Reference for extending degree centrality to multilayer, neighbors,
connective redundancy and relevance: Berlingerio 2011 "Foundations of
multidimensional..."

##### Multidegree

* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers

* Neighbors/neighborhood (number of unique actors directly connected to each focal)

Neighbors = degree within a network layer
But across a multilayer network with multiple layers, some neighbors are repeated.

##### Graph strength

Finally, some weighted variables:

* eigenvector centrality, summed across layers as described in Boccaletti,
Stefano, et al. "The structure and dynamics of multilayer networks." Physics
Reports 544.1 (2014): 1-122.

##### Redundancy/relevance

* Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties

* Relevance: neighborhood of specific layer  / neighbourhood of full ml net. This is the proportion of neighbors present on the layer of focus. Comparing across, it tells you which layers are most important for each individual.

##### Layer similarity

Then there will be some layer similarity. Right now it's just a correlation of each season's asnipe SRI matrix

>>>>

For each multilayer network, we calculated four metrics.These included:
multidegree, graph strength, redundancy/relevance, and  layer similarity.

<!-- GOING
TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON
EXPLAINING THESE).
-->

<!-- 
ALR: Reference for extending degree centrality to multilayer, neighbors,
connective redundancy and relevance: Berlingerio 2011 "Foundations of
multidimensional..."
-->

* Multidegree
* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers
* Neighbors/neighborhood (number of unique actors directly connected to each focal): Neighbors = degree within a network layer. But across a multilayer network with multiple layers, some neighbors are repeated. 
* Graph strength
* Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties
* Relevance: neighborhood of specific layer  / neighbourhood of full ml net. This is the proportion of neighbors present on the layer of focus. Comparing across, it tells you which layers are most important for each individual. 
* layer similarity
